Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-31 ms/main.tex
sympy + notebook - add more condition to the proof

If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
\begin{equation} \label{eq:eigenvalues}
  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
\end{equation}
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
\begin{aligned}
 \alpha_2 > 
 \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
\alpha_1 \;.
\end{aligned}
\end{equation}

\end{appendices}

>>>>

If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda \frac{(X+Q)}{\bar{w}} + \frac{XQ - YZ}{\bar{w}^2}$; At $\lambda = 1$ the characteristic polynomial is equal to:
\begin{equation} \label{eq:characteristic_at_1}
  1-\frac{X+Q}{\bar{w}} + \frac{XQ-YZ}{\bar{w}^2}.
\end{equation}
This polynomial has at least one real root since 
\begin{equation} \label{eq:delta}
  \Delta = \frac{(X+Q)^2}{\bar{w}^2}-\frac{4XQ-4YZ}{\bar{w}^2}=\frac{(X-Q)^2+4YZ}{\bar{w}^2} > 0.
\end{equation}
Since the characteristic polynomial is second order polynomial with leading positive coefficient, if the value at 1 is greater than zero, we know that both roots can be either greater or smaller than 1.
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that the characteristic polynomial is positive at $\lambda = 1$ if 
\begin{equation} \label{eq:both_roots_greater_or_smaller_than_1_condition}
\begin{aligned}
 \alpha_2 < \alpha_1 \;.
\end{aligned}
\end{equation}
Now we know when all the roots are either smaller or greather than 1. We would like to know when all the roots are smaller than 1.
All the roots are smaller than 1 when the slope at 1 is positive. 
Using SymPy we get that the slope is positive when:
\begin{equation} \label{eq:eigenvalues_smaller_than_1_condition}
  \begin{aligned}
   c < &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \\
   OR \\
   c > &\gamma_1 - \frac{(T_B-T_A)b(1-\alpha_1)}{2-T_B} \, AND\, c<\frac{-g}{h}
  \end{aligned}
  \end{equation}
\end{appendices}
